First looks at RF and MI

### 2025-08-13 2-code/x-old/pr_ml/240804_initial_RF.Rmd
reorganize old script files

>>>>

#### 240808 - adding on: how do models for transect location vary between regions? {.tabset}

make_rf_model_by_subset <- function(var, data){

  # 3) Define a recipe
  recipe <- recipe(formula, data = data) %>%
    step_integer(all_nominal_predictors()) %>% # integerize all dbl
    step_corr(all_predictors()) %>% # check correlations between predictors and remove any strong correlations
    step_normalize(all_predictors(), -all_outcomes()) # normalize non-normally distributed predictors

  # 5) Run the  model
  rf_model <- wf %>%
    update_model(rf_spec) %>%
    fit(data = data)

  ## Extract predictions
  predictions <- predict(rf_model, data) %>% rename("predicted" = .pred_class)

  ## Bind predictions to data
  prediction_df <- bind_cols(data, predictions)

  ## Return two things: how good the model did and which variables are most important
  return(list(predictions = prediction_df,
                feature_importance = fi0))
}

# Wrapper function for plotting
plot_rf_results_by_subset <- function(var, data) {

  # Call the make_rf_model function
  model_results <- make_rf_model_by_subset(var, data)

##### Transect location for CB

```{r}
plot_rf_results_by_subset("transect", df %>% filter(region == "CB"))
```

##### Transect location for WLE

```{r}
plot_rf_results_by_subset("transect", df %>% filter(region == "WLE"))
```

```{r}

both_fi_by_region <- bind_rows(make_rf_model_by_subset("transect", df %>% filter(region == "CB"))$feature_importance %>% mutate(region = "CB"), 
          make_rf_model_by_subset("transect", df %>% filter(region == "WLE"))$feature_importance %>% mutate(region = "WLE"))

both_fi_by_region_trim <- both_fi_by_region %>% 
  group_by(region) %>%
  filter(fi_n > (fi_n[predictor == "white_noise"])) %>%
  ungroup()

var_colors <- PNWColors::pnw_palette("Bay", n = length(unique(both_fi_by_region_trim$predictor)))

both_fi_by_region_trim %>% 
  mutate(fi = fi_n * 100) %>% 
  ggplot(aes(x = fi_n * 100, 
             y = reorder(predictor, fi_n), 
             fill = predictor)) + 
  geom_col(alpha = 0.8, show.legend = F, width = 0.7) + 
  scale_fill_manual(values = var_colors) + 
  facet_wrap(~region, nrow = 1) +
  labs(x = "Feature Importance (%)", 
       y = "", fill = "") 
```
